The necessity of hypermedia RDF and an approach to achieve it

### 2012-04-13 eswc-2012/workshop2.tex
redo RaUL role again
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@228 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{itemize}

@@

\item A factor encompassing RaUL templates.

  The RaUL\cite{raul} goes beyond HTTP GET queries, which is what the
  \textsf{LT} factor is about, but can be used to formulate templated
  queries similar to those in HTML, or indeed to generate HTML
  fragments for the same purpose. This is also enables useful
  interactions, albeit quite different from those of this paper.

\end{itemize}

>>>>

\begin{enumerate}

@@

\item A factor encompassing RaUL \cite{raul} templates.

  RaUL goes beyond HTTP GET queries, which is what the \textsf{LT}
  factor is about. The interaction RaUL enables are quite different
  from those discussed in this paper and are not captured by any of
  the current factors.

\end{enumerate}
